---
title: ''
author: "Fraser Interior Area Sockeye Stock Assessment"
date: "Report generated: `r Sys.Date()`"
output: 
  word_document: 
    reference_docx: "sonar_inseason_styles-01.docx"
---

```{r echo=F, include=F}
################################                     READ ME FIRST OR ELSE YOU WILL BE SAD                      ################################

# Hello! Welcome to the R script that generates in-season roving reports! 
# This script was made by K. Davidson in Aug 2021.


#--------- SOME NOTES ON THE ORGANIZATION OF THIS SCRIPT: 
# This script was written to be able to generalize across any roving project Excel data entry file **provided they are the same format as the 2021 files**. However, look for the << >> symbols in this script. These indicate lines of code that you have to customize. Follow the instructions below to customize the code. You shouldn't have to customize anything other than these three items:
# 1. Working directory
#    How to: Click Session > Set Working Directory > Chose Directory... > navigate to the folder on your computer where the Excel data file of                interest is stored. In the console window below, you will see an address appear, something like setwd("~/ANALYSIS/data/sonar_data").              I would recomment copy-pasting this into your script at the top, in place of where my working directory is in the R code chunk                   below. That is because you will have to re-set it each time you open the script anew; by pasting it into your script now, it will                save you time in the future!
# 2. Excel file name for each project
#    How to: In the code chunk below, you will see the following command:  counts.raw <- read_excel("Stellako_Sonar_tool_2020.xlsm", sheet="Data              entry", skip=4, col_names=T). The piece in the quotation marks, "Stellako_Sonar_tool_2020.xlsm", is what you will need to change for              each new project roving file. For example, if you want to load the Quesnel Roving 2021 file, you will have to replace                            "Early Stuart Roving_Daily_Report_2021.xlsm" with "Quesnel Roving_Daily_Report_2021.xlsm". All of the remaining pieces of code can               stay the same. 
# 3. Excel file output at the end
#    How to: In the code chunk you will see the final output:  saveWorkbook(wb, file = "EStu_inseason_2021.xlsx", overwrite = TRUE). The piece in              the quatation marks, "EStu_inseason_2021.xlsx", is what you need to change for each new project. For example, if you want to export              the Quesnel Roving 2021 file, you will have to replace "EStu_roving_inseason_2021.xlsx" with "Quesnel_roving_inseason_2021.xlsx".                All of the remaining pieces of code can stay the same. 

# Any line that starts with a '#' means it is an annotation and it won't run as part of the code or analysis. This is an easy way to write notes, comments, etc. without having them impact your code. It is similar to starting a line of code with a ' symbol in Excel macro VBA code. Each line of code here has attempted to be annotated in plain language to inform the user of the specific data manipulations occurring in each row. 

# In this specific format (called Rmarkdown), it is an extra step in the coding process that can take code and directly produce a document in either MS Word, PDF, or HTML format. Therefore, this script structure looks a bit different than you might expect. See the accompanying word doc 'Cheat Sheet - SONAR RMarkdown In-season ' for more details. 



#--------- TO RUN THE SCRIPT / GENERATE THE REPORT:
# To run each block (or chunk) of R code (the grey shaded boxes that start with ```{r}) independently, press the green 'play' button. This can be useful if you want to troubleshoot a specific part of the code, see a specific piece of the work flow, etc. YOU DON'T HAVE TO DO THIS.

# To generate the report, click the 'Knit' button at the top of the window, just above the top line of code showing. 
```

```{r setup, include=FALSE}
###############################################################################################################################################
                                                         
#                                                                 SET UP  

knitr::opts_chunk$set(echo = TRUE)

# load packages to use
library(tidyverse)     # for everything
library(readxl)        # for read_excel()
library(openxlsx)      # for saveWorkbook() functions
library(pander)        # for table outputs

# Set pander table formatting settings
panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)

# set working directory where Excel roving data entry file is
setwd("~/ANALYSIS/data")                                            # << NEEDS TO BE CUSTOMIZED FOR EACH USER >>

# read in data 
counts.raw <- read_excel("Early Stuart Roving_Daily_Report_2021.xlsm", sheet="Count_entry")                #<<CHANGE FOR EACH PROJECT >>
enviro.raw <- read_excel("Early Stuart Roving_Daily_Report_2021.xlsm", sheet="Environment_entry")           #<<CHANGE FOR EACH PROJECT >>
#project.name <- as.vector(colnames(read_excel("Stellako_Sonar_tool_2020.xlsm", sheet="Data entry", range="E1:E1"))) #<<CHANGE FOR PROJECT >>
#project.year <- lubridate::year(counts.raw$Date[1])


###############################################################################################################################################
                                                         
#                                                             CLEAN THE DATA FOR USE IN R 

#---------- COUNT data 
counts <- counts.raw %>% 
  rename(year=Year,
         stream_name=Stream_ID,
         area=Area,
         stream_shore=`Stream/Shore`,
         run_timing=`Run Timing`,
         watershed_group=`Watershed Group`,
         alias=`This column automatically provides historical/alias name if applicable`,
         area_description=`This column automatically provides a description of the counting area to confirm your choice of \"Area\"  in the previous column`,
         survey_no=`Survey #`,
         date=`Date  (i.e. 20-Oct-14)`,
         survey_type=`Survey Type`,
         calibration_code=`Calibration  code  leave \"blank\" =no calibration                  1= escapement and calibration                     2= calibration only`,
         live_count_obs1=`Live Count Observer 1`,
         live_count_obs2=`Live Count Observer 2`,
         oe=`Observer Efficiency`,
         holding=`% Holding`,
         spawning=`% Spawning`,
         spawned_out=`% Spawned out`,
         behaviour_check=`This column checks if sum of columns( P,Q,R ) = 100%`,
         carc_male=`Carcass Male`,
         carc_fem=`Carcass Female`,
         carc_male_nr=`Male Carcass NR`,
         carc_male_0=`Male Carcass 0%`,
         carc_male_100=`Male Carcass 100%`,
         carc_fem_nr=`Female Carcass NR`,
         carc_fem_0=`Female Carcass 0%`,
         carc_fem_50=`Female Carcass 50%`,
         carc_fem_100=`Female Carcass 100%`,
         carc_jack=`Carcass Jack`,
         carc_ground_unsex=`Ground Carcass Unsexed`,
         carc_aerial_unsex_obs1=`Aerial Carcass Unsexed Observer 1`,
         carc_aerial_unsex_obs2=`Aerial Carcass Unsexed Observer 2`,
         carc_total_unsex=`Total Carcass Unsexed (formula cell, leave blank)`,
         carc_female_check1=`This column checks if sum of columns( Y, Z, AA, AB ) = Carcass Female`,
         carc_female_check2=`This column checks if sum of columns( U,V,W,X ) = Carcass Female`,
         live_tags=`# Live Tags`,
         carc_tags=`# Carcass tags`,
         psc_male=`# PSC Sample Males`,
         psc_female=`# PSC Sample  Females`,
         psc_jack=`# PSC Sample  Jacks`,
         dna_samples=`# DNA Samples`,
         live_chinook=`Live Count Chinook`,
         live_coho=`Live Count Coho`,
         live_kokanee=`Live Count Kokanee`,
         carc_coho=`Carcass Count Coho`,
         carc_chinook=`Carcass Count Chinook`,
         comments=`Comments (specific to one Area within a Stream/Shore) (OK for Comments to exceed width of this column)`) %>%
  select(year:comments) %>%
  mutate_at("oe", as.numeric) %>%
  print()


#---------- ENVIRONMENTAL data
enviro <- enviro.raw %>% 
  rename(year=Year,
         stream_name=StreamID,
         stream_shore=`Stream/Shore`,
         run_timing=`Run Timing`,
         watershed_group=`Watershed Group`,
         alias=`This column automatically provides alias name if applicable`,
         survey_no=`Survey #`,
         survey_type=`Survey type`,
         date=`Date  (e.g. 20-Oct-14)`,
         obs1=`Observer 1`,
         obs2=`Observer 2`,
         peak_spawn_start=`Start PeakSpawn (e.g. 20-Oct-14)`,
         peak_spawn_end=`End PeakSpawn`,
         start_time=`Start Time   (24 hr: hh:mm)`,
         end_time=`End Time`,
         bankfull=`%Bankfull`,
         brightness=Brightness,
         cloud_cover=`%Cloudy`,
         precip_type=`Precip Type`,
         precip_intensity=`Precip Intensity`,
         fish_vis=`Fish Vis`,
         water_temp=`WTemp.`,
         water_clarity=`WClarity`,
         water_gauge_m=`Gauge (m)`,
         comments1=`Comments (relevant to the Stream/Shore as a whole) (OK for Comments to exceed width of column)`,
         comments2=`Additional Comments`) %>% 
  select(year:comments2) %>%
  print()
```

```{r echo=F, include=F}
###############################################################################################################################################

#                                                             DAILY REPORT

#---------- DAILY Report
daily.report <- counts %>% 
  group_by(year, run_timing, stream_shore, survey_type) %>%
  summarize(n_surveys=max(survey_no), 
            male_carcs=sum(carc_male, na.rm=T), female_carcs=sum(carc_fem, na.rm=T), jack_carcs=sum(carc_jack, na.rm=T),
            ground_unsex=sum(carc_ground_unsex, na.rm=T), aerial_unsex=sum(carc_aerial_unsex_obs1, na.rm=T)+sum(carc_aerial_unsex_obs2, na.rm=T),
            fem_nr=sum(carc_fem_nr, na.rm=T), fem_0=sum(carc_fem_0, na.rm=T), fem_50=sum(carc_fem_50, na.rm=T), fem_100=sum(carc_fem_100, na.rm=T), male_nr=sum(carc_male_nr, na.rm=T),
            male_psc=sum(psc_male, na.rm=T), female_psc=sum(psc_female, na.rm=T), jack_psc=sum(psc_jack, na.rm=T),
            n_tags=sum(live_tags, na.rm=T)+sum(carc_tags, na.rm=T), n_dna=sum(dna_samples, na.rm=T)) %>%
  mutate(total_unsex=ground_unsex+aerial_unsex,
         total_carc=total_unsex+male_carcs+female_carcs+jack_carcs) %>%
  select(year:aerial_unsex, total_unsex, total_carc, fem_nr:n_dna) %>%
  print()


###############################################################################################################################################

#                                                             BI-WEEKLY REPORT

# Count aspects of the bi-weekly report
count.biweek <- counts %>% 
  filter(area!="Mouth") %>%
  group_by(year, run_timing, stream_shore, survey_type, survey_no) %>%
  summarize(date=unique(date),
            live_count1=sum(live_count_obs1, na.rm=T), live_count2=sum(live_count_obs2, na.rm=T), 
            male_carcs=sum(carc_male, na.rm=T), female_carcs=sum(carc_fem, na.rm=T), jack_carcs=sum(carc_jack, na.rm=T),
            ground_unsex=sum(carc_ground_unsex, na.rm=T), aerial_unsex1=sum(carc_aerial_unsex_obs1, na.rm=T), aerial_unsex2=sum(carc_aerial_unsex_obs2, na.rm=T),
            fem_nr=sum(carc_fem_nr, na.rm=T), fem_0=sum(carc_fem_0, na.rm=T), fem_50=sum(carc_fem_50, na.rm=T), fem_100=sum(carc_fem_100, na.rm=T),
            oe_avg=mean(oe, na.rm=T), oe_min=min(oe, na.rm=T), oe_max=max(oe, na.rm=T)) %>%
  mutate(average_live_count = round(((live_count1+live_count2)/2),0),
         total_carcasses = male_carcs+female_carcs+jack_carcs+ground_unsex+aerial_unsex1+aerial_unsex2,
         total_unsex = ground_unsex+aerial_unsex1+aerial_unsex2) %>%
  select(year:survey_no, date:live_count2, average_live_count, total_carcasses, male_carcs:aerial_unsex2, total_unsex, fem_nr:oe_max)


# Environmental aspects of the bi-weekly report 
enviro.biweek <- enviro %>% 
  group_by(year, run_timing, stream_shore, survey_type, survey_no) %>%
  summarize(water_temp=water_temp, spawn_start=peak_spawn_start, spawn_end=peak_spawn_end) %>%
  print()


#-------- Join 
biweekly.report <- count.biweek %>%
  left_join(., enviro.biweek, by=c("year", "run_timing", "stream_shore", "survey_type", "survey_no")) %>%
  select(year:fem_100, water_temp, oe_avg:oe_max, spawn_start, spawn_end)
```

```{r echo=F, warning=F, message=F}
daily.report
```

```{r echo=F, warning=F, message=F}
biweekly.report
```

```{r echo=F, include=F}
###############################################################################################################################################

#                                                                  EXPORT TO EXCEL

# Create a blank Excel workbook
wb <- createWorkbook()

# Populate the blank workbook with tabs (i.e., worksheets) for the daily and bi-weekly reports
addWorksheet(wb, "daily_report")
addWorksheet(wb, "biweekly_report")

# Write the summary data generated above to each of those blank worksheets 
writeData(wb, "daily_report", daily.report, startRow = 1, startCol = 1)
writeData(wb, "biweekly_report", biweekly.report, startRow = 1, startCol = 1)

# Export it to an .xlsx file for viewing/further use 
saveWorkbook(wb, file = "EStu_roving_inseason_2021.xlsx", overwrite = TRUE)        # << CHANGE FILE NAME FOR EACH PROJECT >>
```












